On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex
lateset

\begin{proof}
 We assume $w[i]$ is the first bead outside $\hexagon^n_0$
 See Fig.~\ref{fig:ttt_d2}.
 If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
 If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
 If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
 Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.

 We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$. Let $s$ be a element of $S[l+1..m-1]$. If $s = b$, $s$ does not increase binding capability.
 If $s=t$, $s$ is a element of a subsequence $bt^+b$. This subsequence does not increase binding capability according to Theorem~\ref{TTT}. Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.

 The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
 Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
 Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
\end{proof}

@@

	\node[above] at (180:1) {$p_1$};
	\node[above] at (60:2) {$p_2$};
	\node[above,shift=(120:1)]at (60:1) {$p_3$};
	\node[above]at (0:1) {$p_4$};

	\draw (180:1) circle [radius=0.05];
	\draw (60:2) circle [radius=0.05];
	\draw[shift=(120:1)] (60:1) circle [radius=0.05];

@@

      \draw[dashed] (180:2) -- (0:2);
      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
       \draw[dashed, shift=(60:2)] (180:3) -- (0:1);
      \draw[->, blue] (60:0.1) -- (60:0.9);
      \draw[->, blue, shift=(60:1)] (0:0.1) -- (0:0.9);

	\node[above] at (180:1) {$p_1$};
	\node[above] at (60:2) {$p_2$};
	\node[above, shift=(120:1)]at (60:1) {$p_3$};
	\node[above]at (0:1) {$p_4$};

	\draw (180:1) circle [radius=0.05];
	\draw (60:2) circle [radius=0.05];
	\draw[shift=(120:1)] (60:1) circle [radius=0.05];

@@

	\node[below] at (0:0) {$w[i-1]$};
	\node[above] at (60:1) {$w[i]$};
	\node[above, shift=(0:1)] at (60:1) {$w[i+1]$};
	\end{tikzpicture}
    \end{minipage}
    \end{tabular}
    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: (Left) $w[i+1]$ elongated to west, (Right) $w[i+1]$ elongated to east.}
    \label{fig:ttt_d2}
  \end{center}
\end{figure}

>>>>

@@

      \draw[dotted, shift = (60:1)] (0:0) -- (-60:1);

	\node[above,shift=(120:1)]at (60:1) {$p$};

	\draw[shift=(120:1)] (60:1) circle [radius=0.05];

@@

      \draw[dashed] (180:2) -- (0:2);
      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
       \draw[dashed, shift=(60:2)] (180:3) -- (0:1);
      \draw[->, blue] (60:0.1) -- (60:0.9);
      \draw[->, blue, shift=(60:1)] (0:0.1) -- (0:0.9);
       \draw[dotted, shift = (60:1)] (0:0) -- (-60:1);

	\node[above] at (60:2) {$p$};

	\draw (60:2) circle [radius=0.05];

@@

	\node[below] at (0:0) {$w[i-1]$};
	\node[above] at (60:1) {$w[i]$};
	\node[above, shift=(0:1)] at (60:1) {$w[i+1]$};
	\end{tikzpicture}
    \end{minipage}
    \end{tabular}
    \caption{The moment when the transcript steps outside $\hexagon^n_0$.}
    \label{fig:ttt_d2}
  \end{center}
\end{figure}

\begin{proof}
 We assume $w[i]$ is the first bead stabilized outside $\hexagon^n_0$.
 See Fig.~\ref{fig:ttt_d2}.
 The next bead $w[i+1]$ is to be bound for stabilization.
 Hence, it goes to the west  or to the east (Fig.~\ref{fig:ttt_d2}).
 Once $w[i+2]$ is stabilized at $p$, the remaining transcript folds into the zig-zag conformation.
 In order to avoid this or nondeterminism, $w[i+2]$ must form two bonds; it thus decreases binding capability by 1.
 Until when a bead is stabilized outside $\hexagon^{n+1}_0$, binding capability never increases because of arity being 2 and of the Tunnel Troll Theorem.
 This means that, only at most $\#bc(C_0) \leq 2n$ times we can thus expand that hexagonal region.
 In other words, outside $\hexagon^{3n}_0$ the transcript cannot help but fold into the zig-zag conformation. \qed

% 
% If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
% If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
%  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
% If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
% Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.
% 
% We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$. Let $s$ be a element of $S[l+1..m-1]$. If $s = b$, $s$ does not increase binding capability.
% If $s=t$, $s$ is a element of a subsequence $bt^+b$. This subsequence does not increase binding capability according to Theorem~\ref{TTT}. Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.
% 
% The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
% Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
% Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
